\chapter{COMPUTER MODELING OF GENE ABC EXPRESSION}

\section{First Larval Instar}
We can use computer modeling and simulation to predict the cumulative expression of Gene ABC over time. The equation below represents the rate at which Gene ABC is expressed in the first larval instar stage.
\begin{equation}
	\centering
	\int_0^x 4x^2-3x+15, dx
	\label{expression}
\end{equation}
In this formula, $x$ represents time (in days) post egg-hatching. We can compare Equation \ref{expression} to the formulas for other instar stages. 

\section{Rates of Mutation}
Due to the importance of Gene ABC in regulating critical physiological processes in mosquito development, we analyzed the rate of mutation in different strains of mosquito species across various regions in the U.S (see Table \ref{mutation}).

\subsection{Alpha Strain}
The \textit{Alpha} strain tended to have the lowest rates of mutation out of the four groups. This trend was consistent for all U.S. regions tested.

\subsection{Bravo and Delta Strains}
The \textit{Bravo} and \textit{Delta} strains tended to have intermediate mutation rates. 

\subsection{Charlie Strain}
The \textit{Charlie} strain tended to have the highest rates of mutation out of the four groups. This trend was consistent for all U.S. regions tested.

\begin{table}[h!]
\centering
\begin{tabular}{lccccc}
\toprule
& \multicolumn{5}{c}{Region}\\
\cmidrule(l){2-6}
Group & Northeast & Southwest & South & Pacific & N. Central\\
\midrule
Alpha & 1.3 & 1.4 & 1.7 & 2.3 & 1.1 \\
Bravo & 2.7 & 3.3 & 3.6 & 2.5 & 3.4 \\
Charlie & 4.2 & 5.4 & 4.4 & 5.3 & 5.8 \\
Delta & 2.8 & 2.6 & 3.3 & 3.6 & 2.6 \\
\bottomrule
\end{tabular}
\caption{Gene ABC Mutation Rate by U.S. Region}
\label{mutation}
\end{table}


\section{Discussion}
As discussed previously, Gene ABC is critical to the successful development and adult immunity of mosquitoes. The variability we highlight in our regional analysis of Gene ABC mutation rates shows that there may be some significant differences in the expression of this gene. This variability can be due to strain and regional differences.
